---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# walkr

[![CRAN status](https://www.r-pkg.org/badges/version/walkr)](https://cran.r-project.org/package=walkr)
[![Build status](https://travis-ci.org/jeffreyenos/walkr.svg?branch=master)](https://travis-ci.org/jeffreyenos/walkr)
[![Codecov test coverage](https://codecov.io/gh/jeffreyenos/walkr/branch/master/graph/badge.svg)](https://codecov.io/gh/jeffreyenos/walkr?branch=master)

Consider the intersection of two spaces: the complete solution space
to Ax = b and the N-Simplex. The intersection of these two spaces is 
a convex polytope. **walkr** samples from this 
intersection using two Monte-Carlo Markov Chain (MCMC) methods: 
hit-and-run and Dikin walk. **walkr** also provide tools to examine sample 
quality.

# Getting Started

* Install from CRAN (released version):

```{r, eval=FALSE}
  install.packages("walkr")
```
  
* Install from GitHub (development version):  

```{r, eval=FALSE}
  devtools::install_github("andyyao95/walkr")
```

# Sampling Points  
```{r}
  library(walkr)  
  A <- matrix(1, ncol = 3)  
  b <- 1    
  sampled_points <- walkr(A = A, b = b, points = 1000, 
                        method = "dikin", ret.format = "list")   
```
# Visualizing the Sampled Points  

```{r, eval=FALSE}
  explore_walkr(sampled_points)
```